Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-14 paper/section_4_datasets.tex
Move figure
Add example figure

\begin{table}[t]
	\caption {NYTimes800k training, validation, and test splits}
	\label{tab:splits}
	\centering
	\begin{tabularx}{\linewidth}{lXXX}
		\toprule
		  & Training  &   Validation & Test \\
		\midrule
      Number of articles & 434 272 & 3 052 & 8 495 \\
      Number of images  & 764 049 & 7 852 & 22 143 \\
      Start month & Mar 15 & May 19 & Jun 19 \\
      End month & Apr 19 & May 19 & Aug 19 \\
		\bottomrule
	\end{tabularx}
\end{table}

>>>>

\begin{table}[t]
	\caption {NYTimes800k training, validation, and test splits}
	\label{tab:splits}
	\centering
	\begin{tabularx}{\linewidth}{lXXX}
		\toprule
		  & Training  &   Validation & Test \\
		\midrule
      Number of articles & 434 272 & 3 052 & 8 495 \\
      Number of images  & 764 049 & 7 852 & 21 977 \\
      Start month & Mar 15 & May 19 & Jun 19 \\
      End month & Apr 19 & May 19 & Aug 19 \\
		\bottomrule
	\end{tabularx}
\end{table}

\begin{figure*}[t]
   \begin{center}
		\includegraphics[width=0.99\linewidth, frame]{figures/figure_5.pdf}
	\end{center}
   \caption{An example from the NYTimes800k test set. The name ``Chromati'' has
   never appeared in the training data. Words in blue do not appear in the
   article and are hallucinated by the decoder. Words highlighted in red are
   spelling mistakes. Underlined words are those that have been copied by the
   copying mechanism.}
   \label{fig:short}
\end{figure*}
